---
title: "pip20_no8 BCR vj heatmap"
author: "HX"
date: "16/May/2022"
output: html_document
---

# aims
-  plot the V/J usage for heavy or light chain
-  plot the biased V gene usage for heavy and light

# Note
- The source path for "linkseqFunctions.R" need to be changed with your local path
- All the input and out path need to be changed to your local path 

# load the libraries

```{r}
suppressPackageStartupMessages({

  library(ggplot2)
  library(RColorBrewer)
  library(tidyverse)
  library(pheatmap)
  library(Seurat)
  library(ComplexHeatmap)
  library(circlize)
  library(sjPlot)
   library(ggpubr)
  library(SingleR)
  source("/home/hohu/Desktop/LinkSeq1/script/linkseqFunctions.R")
})
```

 
# globle variable
All the input and out path need to be changed to your local path.

```{r}
file_pathBcr<-"/home/hohu/Desktop/LinSeq/data/bcr_lv1/"
# file_pathGex<- "/home/hohu/Desktop/covid_top20_bcr_snakemake/result/summary/pip20/no1/"
file_pathGex<- "/home/hohu/Desktop/LinSeq/data/sc/"

output_path <- "/home/hohu/Desktop/LinkSeq1/result/"
ifelse(!dir.exists(output_path), dir.create(output_path, recursive = T),FALSE)

output_summary<-"/home/hohu/Desktop/LinkSeq1/result/"
ifelse(!dir.exists(output_summary), dir.create(output_summary, recursive = T),FALSE)
```



# V/J gene usage for heavy or light 

```{r}
#fileList <- c("HD2B960","HD2B1500","HD2B3600","p36T1","p36T2","p36T4")
fileList<- c("p36T4")

summary_scBcr <- heatmap_VJ(df_fileList=fileList,df_bcrInputPath=file_pathBcr,
                             rdsInputPath=file_pathGex,outputPath =output_path,type="heavy",vjSummary=output_summary)

summary_scBcr <- heatmap_VJ(df_fileList=fileList,df_bcrInputPath=file_pathBcr,
                             rdsInputPath=file_pathGex,outputPath = output_path,type="light",vjSummary=output_summary)
 
```

 


# biased V gene usage

```{r}

fileList <- c("HD2B960","HD2B1500","HD2B3600","p36T1","p36T2","p36T4")

summary_scBcr <- biased_VHL(df_fileList=fileList,df_bcrInputPath=file_pathBcr,
                                      rdsInputPath=file_pathGex,outputPlot = output_path,
                             outputSummary=output_summary,type="HL")
```



# print session infor
```{r}
sessionInfo()
```
