---
title: "pip20_no7 BCR network"
author: "HX"
date: "16/May/2022"
output: html_document
---

# title:  prepare unassigned heavy  chain cb for levenshtein distance calculation
# reference: https://www.biorxiv.org/content/10.1101/2022.03.01.482462v1.full

## INPUT DATA 
   - sc data from dropseqpipe 
   - BCR from TRUST4 output
   - lv1 corrected BCR use cluster_cb(unique) as new ID 

## Part-1.  
     -  clone network based at single B cell level(used for fig)
     -  heavy CDR3aa with same v,j , same cdr3aa length and >80% similarity are connected   

## Part-2.  
     -  clone network based at single B cell level(to be done)
     -  same light v/j gene 
     - & same heavy v/j , same cdr3aa length and >80% similarity are connected  


# DATE 16/May, 2022


# load library

```{r}
suppressPackageStartupMessages({

  library(ggplot2)
  #library(patchwork)
  library(tidyverse)
  library(Seurat)
  library(RecordLinkage)
  library(igraph)
  library(RColorBrewer)
  #source("/home/hohu/BcrSeqSnakemake/scripts/r/scRepterviorExtention.R")
})
```





# part-1: network analysis at single B cell level 
 - vertices are based on single b cells cluster_cb(lv2 ID), edges are calculated based on cdr3aa similarity
 - GOOD (used for fig)
 

#-------------------------------

fileList<- c("p36T1","p36T2","p36T4","HD2B1500","HD2B3600","HD2B960","p45T2")

df_fileList=fileList
df_bcrInputPath=file_pathBcr
rdsInputPath=file_pathGex
outputPath=ouput_path_plot 
i="p36T1"
#-------------------------------


```{r}

clone_network <-function(df_fileList,df_bcrInputPath,rdsInputPath,outputPath){
  final<- list()
  for(i in  df_fileList ){
    # Read BCR data
    
    bcr_db <- read_tsv(paste0(df_bcrInputPath,i,"_lv1CorrectHeavyBcr.tsv"))
    
    # Read GEX data
    gex_db <- readRDS(paste0(rdsInputPath,i,".rds"))
    
    
    ## Standardize cell IDs
    
    if(i=="p36T1"){
      sample_id<-"p36_T1"
      dpi<- 1
      
    }else if(i=="p36T2"){
      sample_id<-"p36_T2"
      dpi<- 42
    }else if(i=="p36T3"){
      sample_id<-"p36_T3"
      dpi<-89
    }else if(i=="p36T4"){
      sample_id<-"p36_T4"
      dpi<-166
    }else if(i=="p45T2"){
      sample_id<-"p45_T2"
      dpi<-16
    }else if(i=="HD2B1500"){
      sample_id<-"HD2B1500"
      dpi<-0
    }else if(i=="HD2B3600"){
      sample_id<-"HD2B3600"
      dpi<-0
    }else if(i=="HD2B960"){
      sample_id<-"HD2B960"
      dpi<-0
    }else {
      print("now only support p36 time points")
    }
    
    bcr_db$sample<- sample_id
    bcr_db$day<- dpi
    
    ## Standardize cell IDs
    
    # Make cell IDs in BCR match those in Seurat Object   
    # bcr_db$cell_id_unique = paste0(bcr_db$sample, "_", bcr_db$cell_id)
    
    
    # bcr_db$cell_id = sapply(strsplit(bcr_db$sequence_id,"_"), "[",1)   
    
    # NOTE: cell_id becomes the cluster_cb after lv2 correction  
    bcr_db$cell_id_unique = paste0(bcr_db$sample, "_", bcr_db$cell_id)
    bcr_db$cluster_cb_unique = paste0(bcr_db$sample, "_", bcr_db$cluster_cb)
    
    bcr_db$cell_id_unique[1:4]   
    
    # subset heavy bcr for match to have unique cell_id
    # bcr_db <- bcr_db[grep("IGH",bcr_db$v_call ,invert= F),]
    
    
    # match index to find the position of the GEX cells in the BCR data
    match.index = match(Cells(gex_db), bcr_db$cluster_cb_unique)
    
    
    # In this data, not all cells are B cells.
    # What proportion of cells don’t have BCRs?
    mean(is.na(match.index))
    
    
    
    # Just to double check cell ids in the GEX match cells ids in BCR data
    # Should be 1
    mean(Cells(gex_db) == bcr_db$cluster_cb_unique[match.index],na.rm=TRUE)
    ### Label GEX data with BCR data availability
    
    # label whether BCR found in cell
    gex_db$contains_bcr = !is.na(match.index)
    
    ### plot UMAP
    
    
    # List of cells with BCRs
    #highlighted.cells = Cells(gex_db)[which(gex_db$contains_bcr)]
    
    # Plot UMAP with BCR-containing cells
    #pdf(paste0(outputPath,i, "_umap.pdf"))
    
    #p<- DimPlot(object = gex_db, reduction = "umap", cells.highlight = highlighted.cells, label =TRUE, cols="gray", pt.size = 1.0, label.size=8, label.box=TRUE) + NoLegend()
    #print(p)
    #dev.off()
    
    ###########################################################################
    ## Add GEX data to BCR object
    ###########################################################################
    
    
    ### Find the BCR cells in the GEX data
    
    # Match indices to find the position of the BCR cells in the GEX data
    # Different from finding the position of the GEX cells in the BCR data!
    
    match.index = match(bcr_db$cluster_cb_unique, Cells(gex_db))
    
    
    
    # What proportion of BCRs don’t have GEX information?
    mean(is.na(match.index))
    mean(!is.na(match.index))
    
    
    
    
    ### Transfer GEX annotations into the BCR data
    
    
    # Add annotations to BCR data
    cell.annotation = as.character(gex_db@meta.data$SingleR.labels)
    bcr_db$gex_annotation= unlist(lapply(match.index,function(x){ifelse(is.na(x),NA, cell.annotation[x])}))
    bcr_db$gex_annotation[1:5]
    
    # Add UMAP coordinates to BCR data
    #umap1 = gex_db@reductions$umap@cell.embeddings[,1]
    #umap2 = gex_db@reductions$umap@cell.embeddings[,2]
    #bcr_db$gex_umap1= unlist(lapply(match.index, function(x){ifelse(is.na(x),NA, umap1[x])}))
    #bcr_db$gex_umap2= unlist(lapply(match.index, function(x){ifelse(is.na(x),NA, umap2[x])}))
    bcr_db[1:5,] %>%
      select(cell_id,gex_annotation)
    
    
    
    ### Remove cells without GEX data
    
    # Remove cells that didn’t match
    bcr_db = filter(bcr_db, !is.na(gex_annotation))
    
    
    ################################################################
    # UMAP cluster labeling need to be customized for individual sample
    # !!!!!!!!!!!!!!!!!!!!!!!!!
    ################################################################
    ### Ensure information transferred from Seurat object
    
    col_anno = c("Exhausted B cells"="dodgerblue2", "Naive B cells"="firebrick2",
                 "Non-switched memory B cells"="darkolivegreen4","Plasmablasts"="darkgoldenrod2",
                 "Switched memory B cells"="violet","Germline"="darkgrey")
    
    # Plot UMAP from bcr_db
    #pdf(paste0(outputPath,i, "umap_from_bcr_db.pdf"))
    
    #bcr_umap <- ggplot(bcr_db) +geom_point(aes(x = gex_umap1, y = gex_umap2, color = gex_annotation)) +scale_colour_manual(values=col_anno) +theme_bw()
    
    #print(bcr_umap)
    #dev.off()
    
    
    ### Color the UMAP by isotype
    # Plot isotype on UMAP
    # p2<- ggplot(bcr_db) + geom_point(aes(x=gex_umap1,y = gex_umap2,color = isotype)) + theme_bw()
    
    # remove non b cells
    bcr_db <- bcr_db[grep("B cell|Plasmablasts", bcr_db$gex_annotation,invert=F),]  
    
    dim(bcr_db)
    # creat a new column vj_cdr3nt
    bcr_db<-within(bcr_db, 
                   vj_cdr3nt<-paste0(str_split(v_call,",",simplify = T)[,1],"_",str_split(j_call,",",simplify = T)[,1],"_",cdr3) )
    
    bcr_db<-within(bcr_db, 
                   cdr3aa<-substr(junction_aa,2,nchar(junction_aa)-1) )
    bcr_db<-within(bcr_db, 
                   length_cdr3aa<-nchar(cdr3aa) )
    bcr_db<-within(bcr_db, 
                   vj_length_cdr3aa<-paste0(str_split(v_call,",",simplify = T)[,1],"_",str_split(j_call,",",simplify = T)[,1],"_",length_cdr3aa) )
    
    #######################################
    ## collapse redundent bcr by gex_annotation and consensus count
    #######################################
    #---------------------------------------------------------------------------
    # check the cell_id to multiple cluster_cb and select the one with b cell type assignment
    test <- bcr_db %>%group_by(cluster_cb_unique) %>% summarise(n=n()) %>%
      arrange(desc(n)) %>% filter(n>1)
    dim(test)
    test1<-bcr_db%>% filter(cluster_cb_unique %in%test$cluster_cb_unique)
    dim(test1)
    
    data1 <- list()
    uniq_id <- unique(test$cluster_cb_unique)
    for(y in seq_len(length(uniq_id))){
      id.y<- uniq_id[y]
      location.y<- which(id.y==test1$cluster_cb_unique)
      data.y<-test1[location.y,]
      
      test2 <- data.y[grep("B cell|Plasmablasts", test1$gex_annotation,invert=F),]  
      test3 <-test2[ which.max(test2$consensus_count),]
      data1[[y]]<- test3
    }
    collapsed_cell_id <- do.call(rbind,data1)
    dim(collapsed_cell_id )
    
    # recombine the bcr
    unique_cell_id_bcr <- bcr_db%>% filter(! cluster_cb_unique %in%test$cluster_cb_unique)
    final_bcr <- rbind(unique_cell_id_bcr, collapsed_cell_id)
    dim(final_bcr)
    length(final_bcr$cluster_cb_unique)
    ##########################
    # 2nd version lv calculation
    ##########################
    
    uniq_leng_cdr3 <- unique(final_bcr$vj_length_cdr3aa)
    
    
    
    final.y<-list()
    for(y in seq_along(uniq_leng_cdr3) ){
      # string cdr3 list for y
      #y<-1
      uniq_vj_leng_cdr3.y <- uniq_leng_cdr3[y]
      bcr.y <-final_bcr[which(final_bcr$vj_length_cdr3aa==uniq_vj_leng_cdr3.y ) ,]
      dim(bcr.y)
      # extract uniq v,j,cdr3aa 
      #bcr.y1<-  bcr.y %>%select(v_call,j_call,cdr3aa)%>% unique()
      #dim(bcr.y1)
      # cdr3aa stringVector used for lv calculation 
      cdr_list.y <-bcr.y$cdr3aa
      
      # define the similarity threshold >= 80% cdr3aa 
      #threshold.y<- unique(bcr.y$length_cdr3aa)*0.8
      threshold.y <- 0.8
      
      #-------------------------------------------------------------------------------
      # https://stackoverflow.com/questions/5721883/agrep-only-return-best-matches
      # define the "closestMatch" function to calculate the distance and select the 
      closestMatch= function(string,stringVector){
        similarity = levenshteinSim(string, stringVector)
        lv_match <- data.frame(stringVector,similarity)
        
        #  using "filter(similarity==max(similarity) )" to selet multipe max value
        closest<-lv_match %>%
          mutate(cdr3aa_1=string)%>% mutate(cdr3aa_2=stringVector)%>% 
          select(cdr3aa_1,cdr3aa_2,similarity)
      }
      #-------------------------------------------------------------------------------
      
      final.z<-list()
      for(z in seq_along(cdr_list.y)){
        #z<- 1
        cdr3aa.z <- cdr_list.y[z]
        cdr_vect.z <- cdr_list.y[(z+1):length(cdr_list.y)]
        # similarity=0.83333 is equal to lv=2 distance(2 mutation/insertion/deletion)
        bcr_network <- closestMatch(string=cdr3aa.z, stringVector=cdr_vect.z)
        #bcr_network$cdr3aa_string <- cdr3aa.z 
        #bcr_network$cdr3aa_vec <- cdr_vect.z
        bcr_network$cluster_cb_string <- bcr.y$cluster_cb_unique[z] 
        bcr_network$cluster_cb_vec <- bcr.y$cluster_cb_unique[(z+1):length(cdr_list.y)] 
        
        lv.z<-bcr_network %>% filter(similarity>=0.8) %>%filter(cluster_cb_string!=cluster_cb_vec) 
        
        final.z[[z]]<- lv.z
      }
      final.z<- do.call(rbind,final.z)
      final.y[[y]]<-final.z
    }
    final.y<-do.call(rbind,final.y)
    #-------------------------------------
  
    
      #-------------------------------------
    # testing code
    #testing code using small data set lv.z
    #-------------------------------------
    test_edge_cell<- final.y %>% select(cluster_cb_string,cluster_cb_vec)
    dim(test_edge_cell)
    length(test_edge_cell$cluster_cb_string)
    length(test_edge_cell$cluster_cb_vec)
    
    
    
    test_df2<- as.data.frame(table(test_edge_cell)) %>% filter(Freq>0)
    
    dim(test_df2)
    
    uniq_cluster_cb<-final_bcr %>%select(cluster_cb_unique)%>%unique()
    dim(uniq_cluster_cb)
    
   
    
    # if the vertices is less than 1000 use the default layout 
    # else use the fore layout and remove some of the no connection vertices to 
    # low the number of vertice bellow 1000 so default layout can be used 
    
    if(length(uniq_cluster_cb$cluster_cb_unique)<1000){
      
      g_test_all<- graph_from_data_frame(test_df2, directed = F , vertices =uniq_cluster_cb )
      E(g_test_all)$weight <- E(g_test_all)$Freq
      g_test_all
      
      g_test_all_deg<- igraph::degree(g_test_all,mode = c("All"))
      V(g_test_all)$degree <- g_test_all_deg
      which.max(g_test_all_deg)
      
      g_test_all_bw<-betweenness(g_test_all,directed = F)
      V(g_test_all)$betweenness <- g_test_all_bw
      V(g_test_all)$betweenness
      which.max(g_test_all_bw)
      
      g_test_all_eig <- evcent(g_test_all)$vector
      V(g_test_all)$Eigen <- g_test_all_eig
      V(g_test_all)$Eigen
      which.max(g_test_all_eig)
      
      # originalMar<- par("mar")
      # https://stackoverflow.com/questions/23050928/error-in-plot-new-figure-margins-too-large-scatter-plot
      
      if(i=="p36T2"){
        pdf(file = paste0(outputPath,i,"lv1_clone_network_allBcr.pdf"))
        
       par(mar=c(1,1,1,1))
        set.seed(1001)
        g1<-plot(g_test_all,edge.color='grey', vertex.label='',
                 vertex.color="green",
                 vertex.size=sqrt(g_test_all_deg)*2,
                 layout=layout.fruchterman.reingold)
        
        set.seed(1001)
        g2<-plot(g_test_all,edge.color='grey', vertex.label='',
                 vertex.color="green",
                 vertex.size=sqrt(g_test_all_deg)*2,
                 layout=layout.fruchterman.reingold)
        
        set.seed(1001)
        g3<- plot(g_test_all,edge.color="grey", vertex.label='',
                  vertex.color="green",
                  vertex.size=g_test_all_eig*10,
                  layout=layout.fruchterman.reingold)
        print(g1)
        print(g2)
        print(g3)
        
        dev.off()
        
      }else{
        pdf(file = paste0(outputPath,i,"lv1_clone_network_allBcr.pdf"))
        
        set.seed(1001)
        g1<-plot(g_test_all,edge.color='grey', vertex.label='',
                 vertex.color="green",
                 vertex.size=sqrt(g_test_all_deg)*2,
                 layout=layout.fruchterman.reingold)
        
        set.seed(1001)
        g2<-plot(g_test_all,edge.color='grey', vertex.label='',
                 vertex.color="green",
                 vertex.size=sqrt(g_test_all_deg)*2,
                 layout=layout.fruchterman.reingold)
        
        set.seed(1001)
        g3<- plot(g_test_all,edge.color="grey", vertex.label='',
                  vertex.color="green",
                  vertex.size=g_test_all_eig*10,
                  layout=layout.fruchterman.reingold)
        print(g1)
        print(g2)
        print(g3)
        
        dev.off()
        
      }
     
  
      
    }else {
      #######################################
      # option1:  use  layout.fruchterman.reingold 
      # remove no edge vertices 
      #######################################
      # extract all vertices with edges
      v_with_edge<- c(test_df2$cluster_cb_string,test_df2$cluster_cb_vec) %>% unique()
      length(v_with_edge)
      
      # subset the vertices with edges infor to fit the layout.fruchterman.reingold
      sub_uniq_cluster_cb<- uniq_cluster_cb %>% filter(cluster_cb_unique %in% v_with_edge)
      dim(sub_uniq_cluster_cb)
      
      
      # creat graph
      g_test_all<- graph_from_data_frame(test_df2, directed = F , vertices =sub_uniq_cluster_cb )
      E(g_test_all)$weight <- E(g_test_all)$Freq
      g_test_all
      
      g_test_all_deg<- igraph::degree(g_test_all,mode = c("All"))
      V(g_test_all)$degree <- g_test_all_deg
      which.max(g_test_all_deg)
      
      g_test_all_bw<-betweenness(g_test_all,directed = F)
      V(g_test_all)$betweenness <- g_test_all_bw
      V(g_test_all)$betweenness
      which.max(g_test_all_bw)
      
      g_test_all_eig <- evcent(g_test_all)$vector
      V(g_test_all)$Eigen <- g_test_all_eig
      V(g_test_all)$Eigen
      which.max(g_test_all_eig)
      set.seed(1001)
      
     
      #pdf(file = paste0(outputPath,i,"lv1_clone_network_allBcr.pdf"))

      set.seed(1001)
      g1<-plot(g_test_all,edge.color='grey', vertex.label='',
             vertex.color="green",
             vertex.size=sqrt(g_test_all_deg)*2,
             layout=layout.fruchterman.reingold)
      
      set.seed(1001)
      g2<-plot(g_test_all,edge.color='grey', vertex.label='',
             vertex.color="green",
             vertex.size=sqrt(g_test_all_deg)*2,
             layout=layout.fruchterman.reingold)
      
      set.seed(1001)
      g3<- plot(g_test_all,edge.color="grey", vertex.label='',
             vertex.color="green",
             vertex.size=g_test_all_eig*10,
             layout=layout.fruchterman.reingold)
      #######################################
      # option2:  use  layout.fruchterman.reingold 
      # by random subset 1000 vertices for plotting 
      #######################################
      # https://ona-book.org/viz-graphs.html
      #https://github.com/igraph/rigraph/issues/110
      
      # random sample 1000 edges
    
      # subset the vertices with edges infor to fit the layout.fruchterman.reingold
      set.seed(1001)
      rSample_uniq_cluster_cb<- sample(uniq_cluster_cb$cluster_cb_unique ,size=1000)
      # extract corresponding edge data
      rSample_test_df2<- test_df2 %>% 
        filter(cluster_cb_string%in%rSample_uniq_cluster_cb)%>%
        filter(cluster_cb_vec%in%rSample_uniq_cluster_cb)
      
      # creat graph
      rSample_g_test_all<- graph_from_data_frame(rSample_test_df2, directed = F , vertices =rSample_uniq_cluster_cb )
      E(rSample_g_test_all)$weight <- E(rSample_g_test_all)$Freq
      rSample_g_test_all
      
      rSample_g_test_all_deg<- igraph::degree(rSample_g_test_all,mode = c("All"))
      V(rSample_g_test_all)$degree <- rSample_g_test_all_deg
      which.max(rSample_g_test_all_deg)
      
      rSample_g_test_all_bw<-betweenness(rSample_g_test_all,directed = F)
      V(rSample_g_test_all)$betweenness <- rSample_g_test_all_bw
      V(rSample_g_test_all)$betweenness
      which.max(rSample_g_test_all_bw)
      
      rSample_g_test_all_eig <- evcent(rSample_g_test_all)$vector
      V(rSample_g_test_all)$Eigen <- rSample_g_test_all_eig
      V(rSample_g_test_all)$Eigen
      which.max(rSample_g_test_all_eig)
      
      
      
      
      set.seed(1001)
      g4<-plot(rSample_g_test_all,edge.color='grey', vertex.label='',
             vertex.color="green",
             vertex.size=sqrt(rSample_g_test_all_deg)*2,
             layout=layout.fruchterman.reingold)
      
      plot(rSample_g_test_all,edge.color='grey', vertex.label='',
             vertex.color="green",
             vertex.size=sqrt(rSample_g_test_all_deg)*2,
             layout=layout.fruchterman.reingold)
            ggsave(filename=paste0(outputPath,i,"lv1_clone_network_allBcr.png"),
                   plot=last_plot(), width=10, height=10, units="cm",dpi=300)
            
      set.seed(1001)
      g5<-plot(rSample_g_test_all,edge.color='grey', vertex.label='',
             vertex.color="green",
             vertex.size=sqrt(rSample_g_test_all_deg)*2,
             layout=layout.fruchterman.reingold)
      
      set.seed(1001)
      g6<- plot(rSample_g_test_all,edge.color="grey", vertex.label='',
             vertex.color="green",
             vertex.size=rSample_g_test_all_eig*5,
             layout=layout.fruchterman.reingold)
      

      
      pdf(file = paste0(outputPath,i,"lv1_clone_network_allBcr.pdf"))
      print(g1)
      print(g2)
      print(g3)
      print(g4)
      print(g5)
      print(g6)
      dev.off()
      #######################################
      # option3:  use  fore layout for large data more than 1000 vertices
      #######################################
      g_test_all_L<- graph_from_data_frame(test_df2, directed = F , vertices =uniq_cluster_cb )
      E(g_test_all_L)$weight <- E(g_test_all_L)$Freq
      g_test_all_L
      
      g_test_all_L_deg<- igraph::degree(g_test_all_L,mode = c("All"))
      V(g_test_all_L)$degree <- g_test_all_L_deg
      which.max(g_test_all_L_deg)
      
      g_test_all_L_bw<-betweenness(g_test_all_L,directed = F)
      V(g_test_all_L)$betweenness <- g_test_all_L_bw
      V(g_test_all_L)$betweenness
      which.max(g_test_all_L_bw)
      
      g_test_all_L_eig <- evcent(g_test_all_L)$vector
      V(g_test_all_L)$Eigen <- g_test_all_L_eig
      V(g_test_all_L)$Eigen
      which.max(g_test_all_L_eig)
      
     
      
      l<-layout_with_drl(g_test_all_L,  options = drl_defaults$default,
                         weights = E(g_test_all_L)$weight,dim=2)
      set.seed(1001)
      g7<-plot(g_test_all_L,edge.color='grey', vertex.label='',
             vertex.color="green",
             vertex.size=sqrt(g_test_all_L_deg)*2,
             layout=l)
      set.seed(1001)
      g8<-plot(g_test_all_L,edge.color='grey', vertex.label='',
             vertex.color="green",
             vertex.size=sqrt(g_test_all_L_deg)*2,
             layout=l)
      set.seed(1001)
      g9<-  plot(g_test_all_L,edge.color="grey", vertex.label='',
             vertex.color="green",
             vertex.size=g_test_all_L_eig*10,
             layout=l)
      outputPlot_moreThan1k<- paste0(outputPath,"lv1_moreThan1kVertices/")
      ifelse(!dir.exists(outputPlot_moreThan1k),dir.create(outputPlot_moreThan1k,recursive = T),FALSE)
      pdf(file = paste0(outputPlot_moreThan1k,i,"lv1_clone_network_allBcr.pdf"))
      
      print(g7)
      print(g8)
      print(g9)
      dev.off()
      
    }
    


    
    #-------------------------------------
    
    
    
    
  }
  final<- do.call(rbind,final)
  #final<- setNames(final,nm =df_fileList )
  return(final)
}

```



# MAIN 

#-------------------------------------------------------------------------------

fileList<- c("p36T1","p36T2","p36T4","HD2B1500","HD2B3600","HD2B960","p45T2")
df_fileList=fileList
df_bcrInputPath=file_pathBcr
rdsInputPath=file_pathGex
outputPath=ouput_path_plot
i  <- "p36T2"

#-------------------------------------------------------------------------------


```{r}
# global variable
file_pathBcr<-"/home/hohu/Desktop/covid_top20_bcr_snakemake/result/summary/pipeline_10/step3/"
file_pathGex<- "/home/hohu/Desktop/covid_top20_bcr_snakemake/result/summary/pip20/no1/"


ouput_path_plot<- "/home/hohu/Desktop/covid_top20_bcr_snakemake/result/plot/pip20/no7_BCRnetwork/"
ifelse(!dir.exists(ouput_path_plot), dir.create(ouput_path_plot, recursive = T),FALSE)

ouput_path_summary<- "/home/hohu/Desktop/covid_top20_bcr_snakemake/result/summary/pip20/no7_BCRnetwork/"
ifelse(!dir.exists(ouput_path_summary), dir.create(ouput_path_summary, recursive = T),FALSE)



# Main
#------------------------------------------------------------------------------

 fileList<- c("p36T1")
# fileList<- c("p36T1","p36T2","p36T4","HD2B1500","HD2B3600","HD2B960","p45T2")
#-------------------------------
clone_network(df_fileList=fileList,df_bcrInputPath=file_pathBcr,
              rdsInputPath=file_pathGex,outputPath=ouput_path_plot) 

```
















# save the seesion infor

```{r}

#-------------------
# https://community.rstudio.com/t/best-practices-for-saving-session-information/44836
#-------------------

library(sessioninfo)
library(pander)
outputSummary<- "/home/hohu/Desktop/covid_top20_bcr_snakemake/result/summary/pipeline_12/no10c_allSc_pureB_sc_integration/"
pander(sessionInfo(), compact = F)

#library(RColorBrewer)
```


