---
title: "pip22c_no2 sc preprocess and integration"
author: "HX"
date: "14/May/2022"
output: html_document
---
 
# aims
   - integrated single cell analysis
 
# Notes: 
  - All the input and out path need to be changed to your local path 
  
# load library 

```{r}

library(Seurat)
library(patchwork)
library(SingleR)
library("celldex")
library(sjPlot)
library(scales)
library(tidyverse)
library(cowplot)
library(ggpubr)
source("/home/hohu/Desktop/LinkSeq1/script/linkseqFunctions.R")

```


# SingleR cell type prediction and split sc for integration
 
# global variable 

```{r}

outputPlot<- "/home/hohu/Desktop/LinkSeq1/result/"
ifelse(!dir.exists(outputPlot),dir.create(outputPlot, recursive = T),FALSE)

outputSummary<- "/home/hohu/Desktop/LinkSeq1/result/"
ifelse(!dir.exists(outputSummary),dir.create(outputSummary, recursive = T),FALSE)

bcrInputPath<-"/home/hohu/Desktop/LinkSeq1/data/bcr_lv1/"
rdsInputPath<- "/home/hohu/Desktop/LinkSeq1/data/sc/"
list.files(rdsInputPath)

```




```{r}


fileList<- c("HD2B1500","HD2B3600","HD2B960","p36T1","p36T2","p36T4","p45T2","p45T5","p16T1B","p18T1")
newName<- c("HD1","HD2","HD1_stD2","p36D4","p36D45","p36D169","p45D24","p45D164","p16D9","p18D13")



# MAIN 

combineScBcr<- combineSc_Bcr_singleR(file_list=fileList, output_summary=outputSummary,
                                     inputBcr=bcrInputPath,inputSc=rdsInputPath)
#######
# separate sc 
#######
sapply(combineScBcr, dim)

HD1_sc <- combineScBcr[["HD1"]] 
HD2_sc <- combineScBcr[["HD2"]]
HD1_stD2_sc <- combineScBcr[["HD1_stD2"]]
p36D1_sc <- combineScBcr[["p36D4"]]
p36D42_sc <- combineScBcr[["p36D45"]]
p36D166_sc <- combineScBcr[["p36D169"]]
p45D16_sc <- combineScBcr[["p45D24"]] 
p45D156_sc <- combineScBcr[["p45D164"]] 
p16D2B_sc <- combineScBcr[["p16D9"]] 
p18D13_sc <- combineScBcr[["p18D13"]]

####################
#  merge all sc
####################
# all sc combine
sc_combine <- merge(HD1_sc,y=c( HD1_stD2_sc,HD2_sc,p36D1_sc,p36D42_sc,p36D166_sc,p45D16_sc,p45D156_sc,p16D2B_sc,p18D13_sc),
                    add.cell.ids = c("HD1","HD1_stD2","HD2","p36D4", "p36D45", "p36D169","p45D24","p45D164","p16D9","p18D13"), project="covid")

table(sc_combine$label.main,sc_combine$sample)
 
sc_combine$sample <- factor(sc_combine$sample, levels = c("HD2","HD1","HD1_stD2","p16D9","p18D13" ,"p36D4", "p36D45", "p36D169","p45D24","p45D164"))

```


 
# Sc integration 
integrate sc data using different combination 
-1a.  All sc samples, all cells

```{r}


####################
# normalization  
####################

# split the dataset into a list of two seurat objects (stim and CTRL)
merge_split <- SplitObject(sc_combine, split.by = "sample")

# normalize and identify variable features for each dataset independently
merge_split.list <- lapply(X = merge_split, FUN = function(x) {
  x <- NormalizeData(x)
  x <- FindVariableFeatures(x, selection.method = "vst", nfeatures = 2000)
})

# select features that are repeatedly variable across datasets for integration
features <- SelectIntegrationFeatures(object.list = merge_split.list)

immune.anchors <- FindIntegrationAnchors(object.list = merge_split.list, anchor.features = features,  dims = 1:10, k.filter = NA)
# this command creates an 'integrated' data assay
immune.combined0 <- IntegrateData(anchorset = immune.anchors)

# specify that we will perform downstream analysis on the corrected data note that the
# original unmodified data still resides in the 'RNA' assay
DefaultAssay(immune.combined0) <- "integrated"

# Run the standard workflow for visualization and clustering
immune.combined0 <- ScaleData(immune.combined0, verbose = FALSE)
immune.combined0 <- RunPCA(immune.combined0, npcs = 30, verbose = FALSE)
immune.combined0 <- RunUMAP(immune.combined0, reduction = "pca", dims = 1:30)
immune.combined0 <- FindNeighbors(immune.combined0, reduction = "pca", dims = 1:30)

immune.combined <- FindClusters(immune.combined0, resolution = 0.5)

immune.combined$sample <- factor(immune.combined$sample, levels =c("HD1","HD2","HD1_stD2","p36D4","p36D45","p36D169","p45D24","p45D164","p16D9","p18D13") )
table(immune.combined$sample)
table(immune.combined$label.main,immune.combined$sample)

# save cluster to meta data
immune.combined$cluster <- Idents(immune.combined)

####################
# save RDS for downstream pipeline  
####################
saveRDS(object =immune.combined, file = paste0(outputSummary,"allSample_sc_BCR_integration.rds"))


```




# pie chart for other cells co-isolated with B cells across infection

```{r}

 
##=========================================================================================####
# merge all for cell type pie chart
##=========================================================================================####

table(immune.combined$label.main, immune.combined$sample)
# set color mannully
all_main_cellTypes<- c("B cells", "CD4+ T cells","CD8+ T cells", "Dendritic cells","NK cells", "Monocytes","T cells",
                       "Basophils","Neutrophils","Progenitors")

all_main_colours<- c( "B cells"="#b2df8a",  "CD4+ T cells"="#762a83", "CD8+ T cells"="#08519c",
                       "Dendritic cells"="#e31a1c","NK cells"="#9ecae1","Monocytes"="#ff7f00","T cells"="#c51b7d",
                       "Basophils"="gray95","Neutrophils"="#deebf7","Progenitors"="grey")

all_main_color <- all_main_colours[order(as.integer(names(all_main_colours)))]

pie_df <- prop.table(table(immune.combined$label.main, immune.combined$sample), margin = 2) %>%
  as.data.frame() %>%  rownames_to_column()%>% mutate(percentage=round(Freq*100,digits = 2))


colnames(pie_df) <- c("nubmer","mail.label","sample","Freq","percentage")
pie_df$sample <- factor(pie_df$sample ,  levels =c("HD1","HD2","HD1_stD2","p36D4","p36D45","p36D169","p45D24","p45D164","p16D9","p18D13")  )
pie_df$mail.label <- factor(x=pie_df$mail.label, levels = c("B cells","Dendritic cells", "Progenitors","CD4+ T cells","CD8+ T cells","T cells",
                                                             "Monocytes","NK cells","Neutrophils",  "Basophils" ))
head(pie_df)
pie_df1<- pie_df %>% mutate(
  phase=ifelse(sample=="HD1"|sample=="HD2","HD",
               ifelse(sample=="p36D4"|sample=="p16D9"|sample=="p18D13","Acute infection",
                      ifelse(sample=="p36D45"|sample=="p45D24","Convalescence",
                             ifelse(sample=="p36D169"|sample=="p45D164","Post COVID-19","HD_stimulate"))))) %>% 
  mutate(phase_main=ifelse(sample=="HD1"|sample=="HD2"|sample=="p36D169"|sample=="p45D164","HD/Post COVID-19",
               ifelse(sample=="p36D4"|sample=="p16D9"|sample=="p18D13","Acute infection",
                      ifelse(sample=="p36D45"|sample=="p45D24","Convalescence","HD_stimulate")))) %>% 
  mutate(phase_main_short=ifelse(sample=="HD1"|sample=="HD2"|sample=="p36D169"|sample=="p45D164","HD/Late conva.",
               ifelse(sample=="p36D4"|sample=="p16D9"|sample=="p18D13","Acute infection",
                      ifelse(sample=="p36D45"|sample=="p45D24","Early conva.","HD_stimulate"))))



pie_df1$phase <- factor(pie_df1$phase, levels = c("HD_stimulate", "Acute infection","Convalescence" ,"Post COVID-19","HD"  ))
pie_df1$phase_main <- factor(pie_df1$phase_main, levels = c("HD_stimulate", "Acute infection","Convalescence" ,"HD/Post COVID-19"  ))
pie_df1$phase_main_short <- factor(pie_df1$phase_main_short, levels = c("HD_stimulate", "Acute infection","Early conva." ,"HD/Late conva."  ))



My_Theme2 = theme(
  text=element_text(size=15,  face="bold"),
  plot.title = element_text(color="black", size=200, face="bold"),
  axis.title.x =element_blank(),
  axis.title.y = element_blank(),
  axis.text.x = element_blank(),
  axis.text.y = element_blank())


# https://stackoverflow.com/questions/42489277/multiple-ggplot-pie-charts-with-whole-pies
pie_df$sample<- factor(pie_df$sample, levels = c("HD1","HD2","HD1_stD2","p16D9","p18D13","p36D4","p36D45","p45D24","p36D169","p45D164"))

#--------------------------------------------------------------------
 

pie3<- ggplot(data = pie_df1, aes(x = "", y = percentage, fill =  mail.label )) +
  geom_bar(stat = "identity", position = position_fill()) +
  geom_text(aes(label = ""), position = position_fill(vjust = 0.5)) +
  coord_polar(theta = "y") +
  facet_wrap(~ phase_main, ncol = 1)  +
  My_Theme2 +
  theme(legend.position='none') +
  guides(fill=guide_legend(nrow=5, byrow=TRUE)) +
  scale_fill_manual(values = all_main_color)  

pie3



ggsave(filename=paste0(outputPlot,"pie3.png"),
       plot=pie3, width=round(length(unique(immune.combined$sample)))*2.8, height=round(length(unique(immune.combined$sample)))*2.8, units="cm",dpi = 300)

```


# grouped barplot for other cells co-isolated with B cells across infection
 
```{r}
 
# https://www.datanovia.com/en/blog/awesome-list-of-657-r-color-names/
sampleColours = c("HD1_stD2"="#6a51a3","HD1"="blue", "HD2"="#33658A",
                  "p36D4"="#e31a1c","p36D45"="#33a02c","p36D169"="#ff7f00",
                  "p45D24"="#F26157","p45D164"="#20b2aa","p16D9"="mistyrose2","p18D13"="mediumorchid2")

# show_col(sampleColours)

sampleColours2 = c("HD_stimulate"="#6a51a3", "Acute infection"="grey", "Convalescence"="#F26157",
                  "HD/Post COVID-19"="#33a02c")

# show_col(sampleColours2)
 
head(pie_df)
pie_df2<- pie_df1  
pie_df2$phase_main <- factor(pie_df2$phase_main , levels = c("HD_stimulate", "Acute infection","Convalescence" ,"HD/Post COVID-19"))


#----------------------
library(plyr)
data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
 return(data_sum)
}
#----------------------
# add error bar
pie_df3 <-pie_df2 %>% filter(sample!="HD1_stD2")

pie_df_erBar<-  data_summary(pie_df3, varname="percentage", 
                    groupnames=c("mail.label", "phase_main"))

pie_df_erBar$mail.label=as.factor(pie_df_erBar$mail.label)
head(pie_df_erBar)

# Default bar plot
p<- ggplot(pie_df_erBar, aes(x=mail.label, y=percentage, fill=phase_main)) + 
  geom_bar(stat="identity", color="black", 
           position=position_dodge()) +
  geom_errorbar(aes(ymin=percentage-sd, ymax=percentage+sd), width=.2,
                 position=position_dodge(.9)) 
# print(p)

# Finished bar plot

My_Theme_bar2 = theme(
  panel.border = element_rect(colour="black", fill = NA),
  strip.text = element_text(size = 4.5),
  panel.background = element_blank(),
  plot.title = element_text(color="black", size=8, face="bold"),
  axis.title.x = element_text(color="black", size=12),
  axis.title.y = element_text(color="black", size=12),
  axis.text.x =  element_text( size=12, hjust=1,  face="bold",angle = 45),
  axis.text.y =  element_text( size=12, face="bold"),
    legend.text = element_text(size=12, face="bold"),
    legend.title = element_text(size=12, face="bold")
  )


barAll<- p+labs(title="Co-isolation of other immune cells", x="Cell types", y = "Percentage")+
   theme_classic() +   My_Theme_bar2+
   scale_fill_manual(values=c("grey","#F26157","#33a02c"))
print(barAll)

ggsave(filename=paste0(outputPlot,"coIsolated_immuneCells_withLable.png"), 
       plot=barAll, width=18, height=10, units="cm",dpi = 300)

# for non B cells population
pie_df_erBar_nonB <- pie_df_erBar %>% filter(mail.label!="B cells")

# Default bar plot FOR Non-B cells 
p_nonB <- ggplot(pie_df_erBar_nonB, aes(x=mail.label, y=percentage, fill=phase_main)) + 
  geom_bar(stat="identity", color="black", 
           position=position_dodge()) +
  geom_errorbar(aes(ymin=percentage-sd, ymax=percentage+sd), width=.2,
                 position=position_dodge(.9)) 

# Finished bar plot

p_nonB_label<- p_nonB+labs(title="Co-isolation of other immune cells", x="Cell types", y = "Percentage")+
   theme_classic() +  My_Theme_bar2+
   scale_fill_manual(values=c("grey","#F26157","#33a02c"))

print(p_nonB_label)

ggsave(filename=paste0(outputPlot,"nonB_coIsolated_immuneCells_withLable.png"), 
       plot=p_nonB_label, width=18, height=10, units="cm",dpi = 300)

```






 
# check the nFeature for DC cells and compare to other cells to check the possibility of doublets

global variable
```{r}
# save those output figs into a separate folder due to the large amount of figs generated
outputPlot_doublets<- paste0(outputPlot,"doublets/") 
ifelse(!dir.exists(outputPlot_doublets),dir.create(outputPlot_doublets),FALSE)
```

Main 


```{r}


immune.combined$label.main<- factor(immune.combined$label.main,
                                   levels = c("B cells","Monocytes","Dendritic cells","CD4+ T cells", "Progenitors", "CD8+ T cells","T cells","NK cells" ,"Basophils","Neutrophils" ))

pdf(file=paste0(outputPlot_doublets,"nFeature.pdf"))
for(i in seq_along(unique(immune.combined$sample))){
  sample.i <- unique(immune.combined$sample)[i]
  Idents(immune.combined) <- immune.combined$sample
  sc<- subset(immune.combined, idents =sample.i )
  
  freq<- as.data.frame(table(sc$label.main, sc$sample))
  # remove cells less than 4 
   mainCelltype <- freq %>% filter(Freq>4)
   mainCellList <- mainCelltype$Var1
  Idents(sc)<- sc$label.main
  sc_main <- subset(sc, idents = mainCellList )
  # add statistic : median
  # https://github.com/satijalab/seurat/issues/2475
  
  MedianVioSeu <- function() stat_summary(fun.y = median, geom='point', size = 15, colour = "darkred", shape = 95)
  
  pv<- VlnPlot(sc_main, features = "nCount_RNA", split.by = "label.main") +MedianVioSeu() +rremove("legend")
  print(pv)
  
  ggsave(filename=paste0(outputPlot_doublets,sample.i, "nCount.png"), 
       plot=pv, width=12, height=10, units="cm",dpi = 300)
  
  pvF<- VlnPlot(sc_main, features = "nFeature_RNA", split.by = "label.main") +MedianVioSeu() +rremove("legend")
  print(pvF)
  ggsave(filename=paste0(outputPlot_doublets,sample.i, "nFeature.png"), 
       plot=pvF, width=12, height=10, units="cm",dpi = 300)
  

  #################
  # Further subset the BCR expression DC together with B cells
  #################
  
  DC_B <- c("B cells","Dendritic cells")
  DC_B_sc <- subset(sc, idents = DC_B  )
  DC_BCR_positive <- subset(DC_B_sc, subset = IGHM>0)
  ppvC<- VlnPlot(DC_BCR_positive, features = c("nCount_RNA" ), split.by = "label.main") +MedianVioSeu() +rremove("legend")
  print(ppvC)
  
  ppvF <- VlnPlot(DC_BCR_positive, features = c("nFeature_RNA"), split.by = "label.main") +MedianVioSeu() +rremove("legend")
   print(ppvF)
  
  ggsave(filename=paste0(outputPlot_doublets,sample.i, "IGM_positive_DC_B_nCount.png"), 
       plot=ppvC, width=6, height=10, units="cm",dpi = 300)
  
   ggsave(filename=paste0(outputPlot_doublets,sample.i, "IGM_positive_DC_B_nFeature.png"), 
       plot=ppvF, width=6, height=10, units="cm",dpi = 300)

   #################
   # extract DC with or without IGM expression
   #################
   if(sample.i=="p36D4"|sample.i=="p16D9"|sample.i=="p18D13"|sample.i=="HD1_stD2"){
     DC <- subset(sc, idents ="Dendritic cells"  )
     
     # subset sc doesn't express a list of genes 
     #https://github.com/satijalab/seurat/issues/3965
     # https://satijalab.org/seurat/articles/essential_commands.html
     
     fullIso <- c( "IGHD","IGHM","IGHA1","IGHA2","IGHE","IGHG1","IGHG2","IGHG3","IGHG4")
     expr <- FetchData(DC, vars = fullIso)
     fullIso_DC_Neg <- DC[, which(expr == 0)]
     fullIso_DC_Neg$igmExp <-"ig_NegativeDC"

     DC_igM <- subset(DC,   subset = IGHM>0 )
     #DC_igM <- DC[, which("IGHM"> 0|"IGHD"> 0|"IGHA1"> 0|"IGHA2"> 0|"IGHE"> 0|"IGHG1"> 0|"IGHG2"> 0|"IGHG3"> 0|"IGHG4"> 0)]

     DC_igM$igmExp <- "igM_PositiveDC"

   
   DC_merge <- merge(x=DC_igM,y=fullIso_DC_Neg)
   Idents(DC_merge) <- DC_merge$igmExp
   pDC_IgM <- VlnPlot(DC_merge, features = c("nFeature_RNA"), split.by = "igmExp") +MedianVioSeu() +rremove("legend")
   print(pDC_IgM)
   
    ggsave(filename=paste0(outputPlot_doublets,sample.i, "DC_igM_Posi_or_Neg_nFeature.png"), 
       plot=pDC_IgM, width=6, height=10, units="cm",dpi = 300)
    
     pDC_IgM_comb <- VlnPlot(DC_merge, features = c("nCount_RNA","nFeature_RNA","percent.mt"), split.by = "igmExp") +MedianVioSeu() +rremove("legend")
   print(pDC_IgM_comb)
   
    ggsave(filename=paste0(outputPlot_doublets,sample.i, "DC_igM_Posi_or_Neg_AllFeatures.png"), 
       plot=pDC_IgM_comb, width=16, height=10, units="cm",dpi = 300)
   }else{
     print("only focus on early timepoints")
   }

}
dev.off()
```





# HD1_stD2 isotype dotplot

```{r}
Idents(immune.combined)<- immune.combined$sample
 immune.combined_i <- subset(immune.combined,
                                     idents="HD1_stD2")
    table(immune.combined_i$SingleR.labels)
    
 Idents(immune.combined_i)<- immune.combined_i$label.main
    # remove cells < 5 cells
    cellNo<- as.data.frame(table(immune.combined_i$label.main))
    cellNo_main <- cellNo %>% filter(Freq>5)
    cellNo_mainLable <- cellNo_main$Var1
    immune.combined_i_main <-  subset(immune.combined_i,
                                     idents=cellNo_mainLable)
    
    markerForPlot<- c( "IGHD","IGHM","IGHA1","IGHA2","IGHE","IGHG1","IGHG2","IGHG3","IGHG4")
    My_Theme_Dot = theme(
    plot.title = element_blank(),
    axis.title.x =element_blank(),
    axis.title.y = element_blank(),
    axis.text.x = element_text(angle =45,   hjust=1, size=12, face="bold"),
    axis.text.y =  element_text( size=14, face="bold"))
    
   dotPlot<- DotPlot(immune.combined_i_main, assay="RNA",features = markerForPlot, dot.scale = 8, cluster.idents=F) +
      RotatedAxis()
   
     dimplot_flip<- dotPlot  & My_Theme_Dot
  dimplot_flip
 
```

 



-1b.  All sc samples, but pure B cells for both fine and main labels
```{r}
 
####################
#subset pure b cells
####################
 
Idents(sc_combine) <- sc_combine$label.main
sc_combineB <- subset(sc_combine,idents="B cells")
table(sc_combineB$SingleR.labels,sc_combineB$sample)

#######
# further subset b cells by SingleR label
#######

# list and subset fine b sub cell types
fine_cellTypes<- c("Exhausted B cells", "Non-switched memory B cells","Switched memory B cells", "Plasmablasts","Naive B cells")
#immune.combined@meta.data$SingleR.labels <- factor(immune.combined@meta.data$SingleR.labels, levels = fine_cellTypes)

# assign the Idents with fine labels
Idents(sc_combineB)<- sc_combineB$SingleR.labels

fine_sc <- subset(x = sc_combineB, idents =fine_cellTypes, invert = F)

table(fine_sc$SingleR.labels,fine_sc$sample)


####################
# normlization  
####################

# split the dataset into a list of two seurat objects (stim and CTRL)
merge_split <- SplitObject(fine_sc, split.by = "sample")

# normalize and identify variable features for each dataset independently
merge_split.list <- lapply(X = merge_split, FUN = function(x) {
  x <- NormalizeData(x)
  x <- FindVariableFeatures(x, selection.method = "vst", nfeatures = 2000)
})

# select features that are repeatedly variable across datasets for integration
features <- SelectIntegrationFeatures(object.list = merge_split.list)

immune.anchors <- FindIntegrationAnchors(object.list = merge_split.list, anchor.features = features,  dims = 1:30 )
# this command creates an 'integrated' data assay
immune.combined1 <- IntegrateData(anchorset = immune.anchors)

# specify that we will perform downstream analysis on the corrected data note that the
# original unmodified data still resides in the 'RNA' assay
DefaultAssay(immune.combined1) <- "integrated"

# Run the standard workflow for visualization and clustering
immune.combined1 <- ScaleData(immune.combined1, verbose = FALSE)
immune.combined1 <- RunPCA(immune.combined1, npcs = 50, verbose = FALSE)
immune.combined1 <- RunUMAP(immune.combined1, reduction = "pca", dims = 1:50)
immune.combined1 <- FindNeighbors(immune.combined1, reduction = "pca", dims = 1:50)

immune.combinedB <- FindClusters(immune.combined1, resolution = 1)

immune.combinedB$sample <- factor(immune.combinedB$sample, levels =c("HD1","HD2","HD1_stD2","p36D4","p36D45","p36D169","p45D24","p45D164","p16D9","p18D13") )
table(immune.combinedB$sample)
table(immune.combinedB$label.main,immune.combinedB$sample)

# save cluster to meta data
immune.combinedB$cluster <- Idents(immune.combinedB)

####################
# save RDS for downstream pipeline  
####################
saveRDS(object =immune.combinedB, file = paste0(outputSummary,"allSample_pureB_BCR_integration.rds"))


```











```{r}

# QC
table(immune.combinedB$SingleR.labels,immune.combinedB$sample)

Idents(immune.combinedB) <- immune.combinedB$sample

table(Idents(immune.combinedB) )
```

# check the BCR gene expression 

```{r}
outputPlot_dot_isoFull<- paste0(outputPlot,"selectedMarkerPlot/isoFull/")
ifelse(!dir.exists(outputPlot_dot_isoFull),dir.create(outputPlot_dot_isoFull, recursive = T),FALSE)

featureList_isoFull <- c( "IGHD","IGHM","IGHA1","IGHA2","IGHE","IGHG1","IGHG2","IGHG3","IGHG4")

# main
 customMarkers_bySampleByCluster(df=immune.combined,markers.to.plot=featureList_isoFull,
                           outputPlotPath=outputPlot,threshold.cell=5)

```




#  Accute infection analysis

## singleR prediction for early infection samples

```{r}
Idents(sc_combine)<-sc_combine$sample 
# subset the early infection
earlyInfection_list<- c("p16D9", "p18D13", "p36D4")
early_infection<- subset(sc_combine, idents=earlyInfection_list)
# load ref data for singleR prediction
    ref_Monaco <- MonacoImmuneData()
    
# subset the sc
table(early_infection$sample)
  # filter cells
  sub_earlyInfection <- subset(early_infection, subset = nFeature_RNA > 150 & nFeature_RNA < 2000) 
  
table(sub_earlyInfection$sample)

 pred.gex_eInf_main<-SingleR(GetAssayData(sub_earlyInfection, assay = "RNA", slot = "data"), ref = ref_Monaco, labels = ref_Monaco$label.main)
 
pred.gex_eInf_fine<-SingleR(GetAssayData(sub_earlyInfection, assay = "RNA", slot = "data"), ref = ref_Monaco, labels = ref_Monaco$label.fine)
    
# assign the cell types to the sc dataset
sub_earlyInfection$label.main<- pred.gex_eInf_main$labels
sub_earlyInfection$label.fine<- pred.gex_eInf_fine$labels

 # save RDS
# saveRDS(sub_earlyInfection,file = paste0(rdsOutput_Summary,"earlyInfectionMerg.rds"))
# per-cell “deltas”
     
    # QC-1: score heatmap QC
    singlR_heatmap<- plotScoreHeatmap(pred.gex_eInf_main)
    singlR_heatmap
   # ggsave(filename=paste0(outputPlot,i,"_singlR_heatmap.png"), plot=singlR_heatmap,width=16, height=8, units="cm",dpi=300)
    # QC-2:  per-cell “deltas”
    #singlR_deltas<- plotDeltaDistribution(pred.gex_eInf_main, ncol = 3)
    #ggsave(filename=paste0(outputPlot,i,"_singlR_deltas.png"), plot=singlR_deltas, width=16, height=16, units="cm",dpi=300)


 ggsave(filename=paste0(outputPlot,"ealryInfection_singleR.png"), plot=singlR_heatmap,
           width=18, height=10, units="cm",dpi=300)



```


# normalization

```{r}
rna2 <- NormalizeData(sub_earlyInfection, normalization.method = "LogNormalize", scale.factor = 10000)

rna2  <- FindVariableFeatures(rna2 , selection.method = "vst", nfeatures = 2000)
 
# Scaling the data
all.genes <- rownames(rna2)
rna2 <- ScaleData(rna2, features = all.genes)

rna2 <- RunPCA(rna2, features = VariableFeatures(object = rna2))

print(rna2[["pca"]], dims = 1:5, nfeatures = 5)

VizDimLoadings(rna2, dims = 1:2, reduction = "pca")

ElbowPlot(rna2)

rna2 <- FindNeighbors(rna2, dims = 1:15)
rna2 <- FindClusters(rna2, resolution = 0.5)

# Look at cluster IDs of the first 5 cells
head(Idents(rna2), 5)

# If you haven't installed UMAP, you can do so via reticulate::py_install(packages =
# 'umap-learn')
rna2 <- RunUMAP(rna2, dims = 1:12)

# note that you can set `label = TRUE` or use the LabelClusters function to help label
# individual clusters
DimPlot(rna2, reduction = "umap")

```


 
```{r}
# remove cells < 5 cells 
Idents(rna2)<- rna2$label.main
cell_ct<-as.data.frame(table(rna2$label.main))
cell_ct_main <- cell_ct %>%filter(Freq>5)
cell_ct_mainList <- cell_ct_main$Var1

accuteInfection_main <- subset(rna2, idents =cell_ct_mainList )

Idents(accuteInfection_main)<- accuteInfection_main$label.main
# remove cells type < 5 
cell.fre<- as.data.frame(table(rna2$label.main))  %>% mutate(pct=Freq/sum(Freq)*100) %>% filter(pct>1)
major.sc <- subset(rna2, idents=cell.fre$Var1)
 
DimPlot_noLb<-DimPlot(major.sc, reduction = "umap",label = F, pt.size = 0.2) 
DimPlot_noLb
 
ggsave(filename=paste0(outputPlot,"earlyInfecMerg_DimPlot_labelMain_noLB.png"),
          plot=DimPlot_noLb, width=16, height=10, units="cm",dpi=300)
 


# combine T cells , CD4 and CD8 T cells

major.sc_mainLabel <- RenameIdents(object = major.sc, `CD4+ T cells` = "All T cells")
#major.sc_mainLabel <- RenameIdents(object = major.sc_mainLabel, `CD8+ T cells` = "All T cells")
major.sc_mainLabel <- RenameIdents(object = major.sc_mainLabel, `T cells` = "All T cells")

DimPlot_mainCell<- DimPlot(major.sc_mainLabel, reduction = "umap",label = TRUE, pt.size = 0.2) 
DimPlot_mainCell
 

ggsave(filename=paste0(outputPlot,"earlyInfecMerg_DimPlot_labelMain_LB_CombTcells.png"),
          plot=DimPlot_mainCell, width=16, height=10, units="cm",dpi=300)
 
 
```









```{r}
 
ridP<- RidgePlot(object =major.sc_mainLabel,  features =c("IGHM"))
ridP

 
# dot plot
   My_Theme_Dot = theme(
    plot.title = element_blank(),
    axis.title.x =element_blank(),
    axis.title.y = element_blank(),
    axis.text.x = element_text(angle =45,   hjust=1, size=20, face="bold"),
    axis.text.y =  element_text( size=20, face="bold"),
    legend.text = element_text(size=20, face="bold"),
    legend.title = element_text(size=20, face="bold")
    )
   
 

cd_genes <- c("IGHD","IGHM","IGHA1","IGHA2","IGHE","IGHG1","IGHG2","IGHG3","IGHG4")
dotPlot<- DotPlot(object = major.sc_mainLabel, features = cd_genes) + RotatedAxis() + My_Theme_Dot
dotPlot 

 ggsave(filename=paste0(outputPlot,"dotPlotIsoFull_earlyInfecMerg_labelMain_CombTcells.png"),plot=dotPlot, 
          width=length(cd_genes)*2.5, height=length(unique(major.sc_mainLabel$label.main))*1.28 , units="cm",dpi = 300 )
      
    
```





# print session infor
```{r}
sessionInfo()
```


